\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in R

### 2014-01-13 papers/jss/article.Rnw
underscore FTW
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@764 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\Sexpr{m} data sets can be converted to Protocol Buffers
(\Sexpr{format(100*m/n,digits=1)}\%) without loss of information. Upon closer
inspection, all other datasets are objects of class \texttt{nfnGroupedData}.
This class represents a special type of data frame that has some additional 
attributes used by the \pkg{nlme} package, among which a \emph{formula} object.
Because formulas are R \emph{language} objects, they have little meaning to
other systems, and are not supported by the \texttt{rexp.proto} descriptor.
When \texttt{serialize_pb} is used on objects of this class (or other objects
containing unsupported data types), it will serialize all other values and 
attributes of the object, but skip over the unsupported types with a warning.

>>>>

\Sexpr{m} data sets can be converted to Protocol Buffers
(\Sexpr{format(100*m/n,digits=1)}\%) without loss of information. Upon closer
inspection, all other datasets are objects of class \texttt{nfnGroupedData}.
This class represents a special type of data frame that has some additional 
attributes used by the \pkg{nlme} package, among which a \emph{formula} object.
Because formulas are R \emph{language} objects, they have little meaning to
other systems, and are not supported by the \texttt{rexp.proto} descriptor.
When \texttt{serialize\_pb} is used on objects of this class (or other objects
containing unsupported data types), it will serialize all other values and 
attributes of the object, but skip over the unsupported types with a warning.
